Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
example reversed paths

\begin{remark}
\label{rem:propertiesSurface}
The following observations are useful for the computation of examples.
\begin{itemize}
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\item The number of boundary components of~$\surface(\bar Q)$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number~$b$ of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface(\bar Q)$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$).
      Indeed, ~$g=\frac{2-\chi(\surface(\bar Q))}{2}$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components with disks.  
      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
      The above formula for~$g$ follows.
\end{itemize}
\end{remark}

@@

\begin{example}[Reversed paths]
\label{exm:reversedPath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}

\begin{example}[Double paths]
\label{exm:doublePath}
Consider the family of ``double paths quivers'' indicated in \fref{fig:doublePathsQuivers}.

@@

The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Therefore, the corresponding surfaces have $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.

@@

>>>>

\begin{remark}
\label{rem:propertiesSurface}
The following observations are useful for the computation of examples.
\begin{itemize}
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary, while infinite cyclic straight walks yield punctures.
\item The dissection~$\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\item The number~$p$ of punctures of~$\surface(\bar Q)$ is the number of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
\item The number~$b$ of boundary components of~$\surface(\bar Q)$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossoming vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number~$b$ of boundary components of~$\surface(\bar Q)$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface(\bar Q)$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b - p + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
      Indeed, $2g = 2-\chi(\surface(\bar Q))$, where~$\chi(\surface(\bar Q))$ is the Euler characteristic of~$\surface(\bar Q)$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface(\bar Q)$ on which we fill the boundary components and the punctures with disks.  
      The number of faces of this cellular decomposition is~$b$, its number of edges is~$|Q_0|$ and its number of vertices is the number of finite straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1|$.
      The above formula for~$g$ follows.
\end{itemize}
\end{remark}

@@

\begin{example}
\label{exm:reversedPath}
Consider the family of ``reversed paths quivers'' indicated in \fref{fig:reversedPathsQuivers}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.45]{reversedPathsQuivers}}
	\caption{The reversed paths quivers with~$1, 2, 3, 4$ vertices.}
	\label{fig:reversedPathsQuivers}
\end{figure}

The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
Therefore, the corresponding surfaces have $1$ boundary component and genus~$0$.
The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.4]{reversedPathsSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the reversed paths with~$1, 2, 3, 4$ vertices.}
	\label{fig:reversedPathsSurfaces}
\end{figure}

\begin{example}
\label{exm:doublePath}
Consider the family of ``double paths quivers'' indicated in \fref{fig:doublePathsQuivers}.

@@

The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Therefore, the corresponding surfaces have no punctures and
\begin{itemize}
\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $2$ boundary components and genus~$|Q_0|/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.

@@

\vincent{Add a description and a schematic representation of the flip in the accordion complex and in the slalom complex.}
